Cosmology with Weak Lensing photometric surveys: constraints with redshift tomography of non--Gaussian statistics

### 2016-04-18 photoz_paper/paper.tex
fix typo

\begin{abstract}
Weak gravitational lensing is becoming a mature technique to constrain cosmological parameters, such as the dark energy equation of state $w$. When analyzing galaxy surveys, redshift information has proven to be a valuable addition to angular shear correlations. We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for a LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments. We find that the addition of peak counts and moments to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet. We also find that most the cosmological information on $w$ is contained in the highest redshift galaxies, with redshift tomography further improving the constraints by only 15\% to 30\%. The improvement obtained with redshift tomography is much bigger when considering the constraints on $(\Omega_m,w)$ using the convergence power spectrum. We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints. We find that different statistics lead to different bias directions in parameter space, leaving a window open for self--calibration. 
\end{abstract}

>>>>

\begin{abstract}
Weak gravitational lensing is becoming a mature technique to constrain cosmological parameters, such as the dark energy equation of state $w$. When analyzing galaxy surveys, redshift information has proven to be a valuable addition to angular shear correlations. We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for a LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments. We find that the addition of peak counts and moments to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet. We also find that most the cosmological information on $w$ is contained in the highest redshift galaxies, with redshift tomography further improving the constraints by only 15\% to 30\%. The improvement obtained with redshift tomography is much bigger when considering the constraints on $(\Omega_m,\sigma_8)$ using the convergence power spectrum. We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints. We find that different statistics lead to different bias directions in parameter space, leaving a window open for self--calibration. 
\end{abstract}
